Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-02-11 chapters/chapter06.tex

\begin{remark}{Infinite hidden Markov models\label{ref:infinite_hidden_markov}}
Hidden Markov model (HMM) $\left\{ X\left(t\right):\; t=1,2,\ldots\right\}$ defines a probability distribution over sequences of observations $\mathbf{X}=\left\{ X(1), \ldots,X(t) \right\}$ by invoking another sequence of unobserved (\emph{hidden}) discrete state variables $\left\{ C\left(t\right):\; t=1,2,\ldots\right\}$.

>>>>

\begin{remark}{Infinite Hidden Markov models\label{ref:infinite_hidden_markov}}
A Hidden Markov model (HMM) $\left\{ X\left(t\right):\; t=1,2,\ldots\right\}$ defines a probability distribution over sequences of observations $\mathbf{X}=\left\{ X(1), \ldots,X(t) \right\}$ by invoking another sequence of unobserved (\emph{hidden}) discrete state variables $\left\{ C\left(t\right):\; t=1,2,\ldots\right\}$.
